---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# shoeScanR

<!-- badges: start -->
<!-- badges: end -->

The goal of shoeScanR is to ...

## Installation

Install the development version of shoeScanR from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("CSAFE-ISU/shoeScanR")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(shoeScanR)
## basic example code
```

- minimal example of two scan parts that show the same shoe 
- visualize, and
- work through alignment process


The following examples are using sony shoes (and absolute file paths, which is a big NO), that's going to be too complicated for the final README:

```{r}
# read scans
sony1 <- read_stl("/Users/heike/Documents/Data/shoe3d/data-raw/My_Scans/Asic06_03_19.stl")
sony2 <- read_stl("/Users/heike/Documents/Data/shoe3d/data-raw/My_Scans/SonyL_20190702.stl")

# center the scans
sony1 <- center3d(sony1)
sony2 <- center3d(sony2)
```
